### 2021-02-28 math/ia_2021/paper.tex
ia work

$SS_{res} = \sum_{i} (y_i - p_i)^2 = \sum_{i} e_i^2$, \footnote{$\sum_i i$ would mean that all values i 
are summed} where $e_i$ is the error term, equal to the difference of a data point $y_i$ 
and its corresponding predicted value $p_i$.

>>>>

$SS_{res} = \sum_{i} (y_i - p_i)^2 = \sum_{i} e_i^2$, \footnote{$\sum_{i=1}^n x_i$ means that all values of 
x are summed, beginning from $x_1$ and ending at $x_n$} where $e_i$ is the error term, equal to the difference of a data point $y_i$ 
and its corresponding predicted value $p_i$.
